*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayPlot" to "scramblase_assay_plot";

```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
```

@@

with the same modifying arguments to the function as for `scramblaseAssayPlot`.

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::readScramblaseInputFile(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 6,
  bottomPanel = 7,
  leftPanel = 1,
  rightPanel = 2,
  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblaseAssayPlot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblaseAssayPlot("inputTable.txt",
  generation_of_algorithm = 1,
  splitByExperiment = FALSE) + 
xlim(0, 2)
```

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 1C
by `scramblaseAssayPlot` in a call to `scramblaseAssayStats`, this is achieved
and produces tabular output represented in Table 1.

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblaseAssayPlot(
    x,
    generation_of_algorithm = 1)
  scramblaseAssayPlot(
    x,
    generation_of_algorithm = 1,
    splitByExperiment = FALSE)
  scramblaseAssayStats(
    x,
    generation_of_algorithm = 1, 
    splitByExperiment = FALSE)
}

>>>>

```{r, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
```

@@

with the same modifying arguments to the function as for `scramblase_assay_plot`.

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
x <- flippant:::readScramblaseInputFile(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 1,
  bottomPanel = 3,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 4,
  bottomPanel = 5,
  leftPanel = 1, 
  rightPanel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- AddPanel(
  figure = figure1,
  topPanel = 6,
  bottomPanel = 7,
  leftPanel = 1,
  rightPanel = 2,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
grid.draw(figure1)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
```

@@

```{r, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 1,
  splitByExperiment = FALSE) + 
xlim(0, 2)
```

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 1C
by `scramblase_assay_plot` in a call to `scramblaseAssayStats`, this is achieved
and produces tabular output represented in Table 1.

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    splitByExperiment = FALSE)
  scramblaseAssayStats(
    x,
    generation_of_algorithm = 1, 
    splitByExperiment = FALSE)
}
